% !TeX program = lualatex

% *Author: Filipe Bernardinello*
% *License: Apache 2.0*

\documentclass[letterpaper,10pt]{article}
\usepackage{lib/commands}

\begin{document}

% Header
\createHeader{
    name = {Filipe Bernardinello},
    linkedin = {https://www.linkedin.com/in/bernardinello/},
    phone = {+55 (14) 99999-9999},
    email = {filipebernardinello@gmail.com},
    github = {https://github.com/filipebernardinello},
    address = {Bauru, São Paulo}
}

% Education section
\createEducationSection{
    \EducationItem[
        institution = {São Paulo State University (UNESP)},
        location = {Bauru, São Paulo},
        degree = {Bachelor of Science in Computer Science},
        date = {Feb. 2022 -- Dec. 2025}
    ]
}

% Experience section
\createExperienceSection{
    \ExperienceItem[
        title = {Job Title},
        company = {Company Name},
        date = {Jan. 2020 -- Present},
        location = {City, State}
    ]{
        \Description{Description of the most important responsibility or achievement in this role}
        \Description{Details about a specific project, the technology stack used (e.g., Java, Python), and the outcome}
        \Description{Quantifiable result achieved (e.g., reduced processing time by 20\% or increased revenue by 15\%)}
        \Description{Mention of soft skills or team leadership responsibilities, if applicable}
    }
    
    \ExperienceItem[
        title = {Previous Job Title},
        company = {Previous Company Name},
        date = {Jan. 2018 -- Dec. 2019},
        location = {City, State}
    ]{
        \Description{Description of the main tasks performed in this role}
        \Description{Implementation of a specific feature or system module}
        \Description{Collaboration with other teams or stakeholders to achieve a common goal}
    }
}

% Projects section
\createProjectsSection{
    \ProjectItem[
        name = {Project Name Alpha},
        date = {Jan. 2023 -- Present}
    ]{
        \Description{Brief summary of what the project does and its target audience}
        \Description{Technical details about the architecture (e.g., Microservices, Monolith) and languages used}
        \Description{Specific challenges overcome during development or deployment}
    }

    \ProjectItem[
        name = {Project Name Beta},
        date = {Jun. 2022 -- Dec. 2022}
    ]{
        \Description{Description of the problem this project solves}
        \Description{Tools and frameworks utilized (e.g., React, Spring Boot, Docker)}
        \Description{Outcome or impact of the project (e.g., open source contribution, hackathon winner)}
    }
}

% Research section
\createResearchSection{
    \ResearchItem[
        role = {Research Assistant},
        institution = {University Name},
        date = {Jan. 2021 -- Dec. 2021},
        location = {City, State}
    ]{
        \Description{Summary of the research topic or hypothesis being investigated}
        \Description{Methodology used for experiments or data analysis}
        \Description{Results obtained or papers published as a result of this research}
    }
}

% Skills section
\createSkillsSection{
    \SkillItem[category = {Languages}, skills = {Java, Go, TypeScript, Python, SQL}]
    \SkillItem[category = {Frameworks}, skills = {Spring Boot, Quarkus, Gin, React, PyTorch, LangGraph}]
    \SkillItem[category = {Libraries}, skills = {NumPy, Pandas, Matplotlib}]
    \SkillItem[category = {Databases}, skills = {MongoDB, PostgreSQL, Redis}]
    \SkillItem[category = {Tools \& Technologies}, skills = {Docker, Kafka, Pulsar, GraphQL, RabbitMQ, AWS, GraalVM}]
    \SkillItem[category = {Methodologies}, skills = {Agile, Scrum, Kanban, CI/CD}]
}

\end{document}